---
title: "NonEdu"
author: "Maitreya Wagh"
date: "6/3/2018"
output:
  html_document:
    keep_md: yes
---



```{r}
Edu <- read.csv("../data/vista/2018-05-23-vista-2013-16/VISTA_2012_16_v1_SA1_CSV/JTE_VISTA12_16_SA1_V1.csv")

```


Profession based on main activity and age
``{r}
```{r}
Person <- Persons[Persons$PERSID %in% Edu$PERSID, ]
SingEduPerson <- subset(as.data.frame(table(Edu$PERSID)), as.data.frame(table(Edu$PERSID))$Freq == 1)
SingEdu <- Edu[Edu$PERSID %in% SingEduPerson$Var1,]
SingEduPerson <- Person[Person$PERSID %in% SingEduPerson$Var1,]
SingEdu <- SingEdu[order(SingEdu$PERSID),]
SingEduPerson <- SingEduPerson[order(SingEduPerson$PERSID),]
SingEdu <- cbind(SingEdu,SingEduPerson)
Edu <- subset(SingEdu, SingEdu$MAINACT=="Primary School"|SingEdu$MAINACT=="Secondary School"|SingEdu$MAINACT=="Full-time TAFE/Uni"|SingEdu$MAINACT=="Part-time TAFE/Uni")
Edu$AgeGroup_RW <- as.factor(Edu$AgeGroup_RW)
Edu$MAINACT<-as.factor(as.character(Edu$MAINACT))
formalsetEdu <- subset(PersonsSuburb,PersonsSuburb$MainAct=="Primary School"|PersonsSuburb$MainAct=="Secondary School"|PersonsSuburb$MainAct=="Full-time TAFE/Uni"|PersonsSuburb$MainAct=="Part-time TAFE/Uni")
names(formalsetEdu)[2] <- "AGE"
names(formalsetEdu)[3] <- "SEX"
names(formalsetEdu)[13] <- "MAINACT"
```




test_data<-subset(PersonsSuburb,PersonsSuburb$Gender=="Female")
test_data<-subset(test_data,test_data$MainAct=="Primary School"|test_data$MainAct=="Secondary School"|test_data$MainAct=="Full-time TAFE/Uni"|test_data$MainAct=="Part-time TAFE/Uni")
test_data$MainAct <- as.factor(as.character(test_data$MainAct))
test_data$EduCat <- as.numeric(test_data$MainAct)
test_data <-test_data[,c(1,2,3,12,14)]
test_data$Rand <- runif(nrow(test_data), 0, 100)
train_data<-subset(Edu,Edu$SEX=="Female")
train_data$EduCat <- as.numeric(train_data$MAINACT)


train_data2 <- subset(train_data,train_data$EduCat==1)
test_data2 <- subset(test_data,test_data$EduCat==1)

training_set <- subset(train_data2,train_data2$AgeGroup_RW==1)
test_set <- subset(test_data2,test_data2$AgeGroup==1)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Act <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$MainAct[j] <- EduCat$Act[i] 
    j=j+1
  }
}
finalset <- test_set

a = 2
for (a in 2:7){
training_set <- subset(train_data2,train_data2$AgeGroup_RW==a)
test_set <- subset(test_data2,test_data2$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Act <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$MainAct[j] <- EduCat$Act[i] 
    j=j+1
  }
}
test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}


for (b in 2:4){
train_data2 <- subset(train_data,train_data$EduCat==b)
test_data2 <- subset(test_data,test_data$EduCat==b)



for (a in 1:7){
training_set <- subset(train_data2,train_data2$AgeGroup_RW==a)
test_set <- subset(test_data2,test_data2$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(traning_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Act <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:10){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$MainAct[j] <- EduCat$Act[i] 
    j=j+1
  }
}
test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}
}


test_data<-subset(PersonsSuburb,PersonsSuburb$Gender=="Male")
test_data<-subset(test_data,test_data$MainAct=="Primary School"|test_data$MainAct=="Secondary School"|test_data$MainAct=="Full-time TAFE/Uni"|test_data$MainAct=="Part-time TAFE/Uni")
test_data$MainAct <- as.factor(as.character(test_data$MainAct))
test_data$EduCat <- as.numeric(test_data$MainAct)
test_data <-test_data[,c(1,2,3,12,14)]
test_data$Rand <- runif(nrow(test_data), 0, 100)
train_data<-subset(Edu,Edu$SEX=="Male")
train_data$EduCat <- as.numeric(train_data$MAINACT)

train_data2 <- subset(train_data,train_data$EduCat==1)
test_data2 <- subset(test_data,test_data$EduCat==1)

a = 0
for (a in 0:7){
training_set <- subset(train_data2,train_data2$AgeGroup_RW==a)
test_set <- subset(test_data2,test_data2$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Act <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$MainAct[j] <- EduCat$Act[i] 
    j=j+1
  }
}
test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}

b=2
for (b in 2:4){
train_data2 <- subset(train_data,train_data$EduCat==b)
test_data2 <- subset(test_data,test_data$EduCat==b)


a = 0
for (a in 0:7){
training_set <- subset(train_data2,train_data2$AgeGroup_RW==a)
test_set <- subset(test_data2,test_data2$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Act <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$ANZSCO1, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$MainAct[j] <- EduCat$Act[i] 
    j=j+1
  }
}
test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}
}
formalsetEdu <- finalset
names(formalsetEdu)[2] <- "AGE"
names(formalsetEdu)[3] <- "SEX"
names(formalsetEdu)[7] <- "ANZSCO1"



```{r, fig.width=15, fig.height=10}
# ggplot(Edu,aes(x=Edu$AgeGroup_RW, fill = Edu$ANZSCO1)) + geom_bar(position = "fill")
# ggplot(finalset,aes(x=finalset$AgeGroup,fill=finalset$MainAct)) + geom_bar(position = "fill")
```
Start Time
```{r, fig.width=15, fig.height=10}

formalsetEdu <- formalsetEdu[order(formalsetEdu$AgentId),]
formalsetEdu$AgeGroup <- as.factor(formalsetEdu$AgeGroup)
dataset2 <- Edu[,c(114,128,11)]
dataset2$MAINACT = factor(dataset2$MAINACT,
                       labels = c(1:4))

test_set <- formalsetEdu[,c(2,13)]

test_set$MAINACT = factor(test_set$MAINACT,
                       labels = c(1:4))
finalerr <- 1000
idealtrees = 0
for (a in 1:20){
line_reg = randomForest(x=dataset2[-3],y=dataset2$STARTIME,ntree = 10*a,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$STARTIME = predict(line_reg, test_set)
err <- sum(abs((aggregate(Edu$STARTIME~Edu$AgeGroup_RW,FUN=mean)[2]-aggregate(formalsetEdu$STARTIME~formalsetEdu$AgeGroup, FUN=mean)[2])/(aggregate(Edu$STARTIME~Edu$AgeGroup_RW,FUN=mean)[2])*100))
if (err<finalerr){
  finalerr=err
  idealtrees = 10*a
}
}
line_reg = randomForest(x=dataset2[-3],y=dataset2$STARTIME,ntree = idealtrees,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$STARTIME = predict(line_reg, test_set)

ggplot(Edu,aes(x=Edu$MAINACT,y=Edu$STARTIME,fill=Edu$AgeGroup_RW))+geom_boxplot() +coord_cartesian(ylim=c(400,700))
ggplot(formalsetEdu,aes(x=formalsetEdu$MAINACT,y=formalsetEdu$STARTIME,fill=formalsetEdu$AgeGroup))+geom_boxplot()
```




Duration
```{r}
# Edu$workDuration <- as.numeric(Edu$workDuration)
# dataset2 <- Edu[,c(114,131,77)]
# 
# dataset2$ANZSCO1 = factor(dataset2$ANZSCO1,labels = c(1:10))
# test_set <- formalsetEdu[,c(2,7)]
# 
# test_set$ANZSCO1 = factor(test_set$ANZSCO1,
#                        labels = c(1: 10))
# 
# 
# finalerr <- 100
# idealtrees = 0
# for (a in 1:20){
# line_reg = randomForest(x=dataset2[-3],y=dataset2$workDuration,ntree = 10*a,weights = Edu$CW_ADJTEWGT_LGA)
# formalsetEdu$workDuration = predict(line_reg, test_set)
# err <- sum(abs((aggregate(Edu$workDuration~Edu$AgeGroup_RW,FUN=mean)[2]-aggregate(formalsetEdu$workDuration~formalsetEdu$AgeGroup, FUN=mean)[2])/(aggregate(Edu$workDuration~Edu$AgeGroup_RW,FUN=mean)[2])*100))
# if (err<finalerr){
#   finalerr=err
#   idealtrees = 10*a
# }
# }
# line_reg = randomForest(x=dataset2[-3],y=dataset2$workDuration,ntree = idealtrees,weights = Edu$CW_ADJTEWGT_LGA)
# formalsetEdu$workDuration = predict(line_reg, test_set)
# 
# 
# 









```








Mode based on Age
```{r}
test_data<-subset(formalsetEdu,formalsetEdu$SEX=="Female")
test_data <-test_data[,c(1,12)]
test_data$Rand <- runif(nrow(test_data), 0, 100)
train_data<-subset(Edu,Edu$SEX=="Female")


training_set <- subset(train_data,train_data$AgeGroup_RW==1)
test_set <- subset(test_data,test_data$AgeGroup==1)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Mode <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:10){
 while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$JTEMODE[j] <- EduCat$Mode[i] 
    j=j+1
  }
}
finalset <- test_set

a = 2
for (a in 2:7){
training_set <- subset(train_data,train_data$AgeGroup_RW==a)
test_set <- subset(test_data,test_data$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Mode <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
  while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$JTEMODE[j] <- EduCat$Mode[i] 
    j=j+1
  }
}

test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}

test_data<-subset(formalsetEdu,formalsetEdu$SEX=="Male")
test_data <-test_data[,c(1,12)]
test_data$Rand <- runif(nrow(test_data), 0, 100)
train_data<-subset(Persons,Persons$SEX=="Male")



a = 1
for (a in 1:7){
training_set <- subset(Edu,Edu$AgeGroup_RW==a)
test_set <- subset(test_data,test_data$AgeGroup==a)
test_set <- test_set[order(test_set$Rand),]
EduCat<-as.data.frame(cumsum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE,weights = training_set$CW_ADPERSWGT_LGA))*100)
EduCat$Mode <- rownames(EduCat)
rownames(EduCat)<-c()
EduCat$Wt <- EduCat$`cumsum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA))/sum(wtd.table(training_set$JTEMODE, weights = training_set$CW_ADPERSWGT_LGA)) * 100`
EduCat <- EduCat[,c(-1)]
j=1
i=1
for (i in 1:13){
  while (test_set$Rand[j]<EduCat$Wt[i]&&!is.na(test_set$Rand[j])){
    test_set$JTEMODE[j] <- EduCat$Mode[i] 
    j=j+1
  }
}

test_set<-test_set[order(test_set$AgentId),]
finalset <- rbind(finalset,test_set)
}

finalset <- finalset[order(finalset$AgentId),]
formalsetEdu <- formalsetEdu[order(finalset$AgentId),]
formalsetEdu <- cbind(formalsetEdu,finalset$JTEMODE)
names(formalsetEdu)[15]<-"JTEMODE"



```


```{r}
Edu$EduCat <- as.factor(Edu$EduCat)
reg <- lm(Edu$JTEDIST~Edu$STARTIME+Edu$SEX+Edu$JTEMODE)
summary(reg)
```

Distance to work
```{r}
dataset2 <- Edu[,c(11,128,82,78)]

dataset2$JTEMODE = factor(dataset2$JTEMODE,
                       labels = c(1:11))
dataset2$MAINACT = factor(dataset2$MAINACT,
                       labels = c(1:4))
test_set <- formalsetEdu[,c(14,13,15)]
test_set$JTEMODE = factor(test_set$JTEMODE,
                       labels = c(1:11))
test_set$MAINACT = factor(test_set$MAINACT,
                       labels = c(1:4))
finalerr <- 1000
idealtrees = 0
for (a in 1:20){
line_reg = randomForest(x=dataset2[-4],y=dataset2$JTEDIST,ntree = 10*a,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$JTEDIST = predict(line_reg, test_set)
err <- sum(abs((aggregate(Edu$JTEDIST~Edu$JTEMODE,FUN=mean)[2]-aggregate(formalsetEdu$JTEDIST~formalsetEdu$JTEMODE, FUN=mean)[2])/(aggregate(Edu$JTEDIST~Edu$JTEMODE,FUN=mean)[2])*100))
if (err<finalerr){
  finalerr=err
  idealtrees = 10*a
}
}
line_reg = randomForest(x=dataset2[-4],y=dataset2$JTEDIST,ntree = idealtrees,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$JTEDIST = predict(line_reg, test_set)

ggplot(Edu,aes(x=Edu$MAINACT,y=Edu$JTEDIST,fill=Edu$AgeGroup_RW))+geom_boxplot() +coord_cartesian(ylim=c(0,25))
ggplot(formalsetEdu,aes(x=formalsetEdu$MAINACT,y=formalsetEdu$JTEDIST,fill=formalsetEdu$AgeGroup))+geom_boxplot()



```


Average Speed

```{r}
Edu$JTESPEED <- (Edu$JTEDIST/Edu$JTE_TravelTime)*60
reg <- lm(Edu$JTESPEED~Edu$STARTIME+Edu$SEX+Edu$JTEMODE+Edu$AGE)
summary(reg)
```

```{r}
dataset2 <- Edu[,c(11,82,186)]
dataset2$JTEMODE = factor(dataset2$JTEMODE,
                       labels = c(1:11))
test_set <- formalsetEdu[,c(14,15)]
test_set$JTEMODE = factor(test_set$JTEMODE,
                       labels = c(1:11))
finalerr <- 1000
idealtrees = 0
for (a in 1:20){
line_reg = randomForest(x=dataset2[-3],y=dataset2$JTESPEED,ntree = 10*a,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$JTESPEED = predict(line_reg, test_set)
err <- sum(abs((aggregate(Edu$JTESPEED~Edu$JTEMODE,FUN=mean)[2]-aggregate(formalsetEdu$JTESPEED~formalsetEdu$JTEMODE, FUN=mean)[2])/(aggregate(Edu$JTESPEED~Edu$JTEMODE,FUN=mean)[2])*100))
if (err<finalerr){
  finalerr=err
  idealtrees = 10*a
}
}
line_reg = randomForest(x=dataset2[-3],y=dataset2$JTESPEED,ntree = idealtrees,weights = Edu$CW_ADJTEWGT_LGA)
formalsetEdu$JTESPEED = predict(line_reg, test_set)
```

```{r, fig.width=15, fig.height=10}
ggplot(Edu,aes(x=Edu$AgeGroup_RW,y=Edu$STARTIME))+geom_boxplot()  + coord_cartesian(ylim=c(400,700))
ggplot(formalsetEdu,aes(x=formalsetEdu$AgeGroup,y=formalsetEdu$STARTIME))+geom_boxplot()


ggplot(Edu,aes(x=Edu$JTEMODE,y=Edu$JTESPEED))+geom_boxplot() + coord_cartesian(ylim=c(0,30))
ggplot(formalsetEdu,aes(x=formalsetEdu$JTEMODE,y=formalsetEdu$JTESPEED))+geom_boxplot()


```



Time taken to reach work in hours
```{r}
formalsetEdu$JTETIME <- formalsetEdu$JTEDIST/formalsetEdu$JTESPEED
formalsetEdu$ReachEduTme <- formalsetEdu$STARTIME + formalsetEdu$JTETIME
formalsetEdu$LeaveEduTime <- formalsetEdu$ReachEduTme+formalsetEdu$workDuration
```




Whole thing for Edu


