---
title: "NonWork"
author: "Maitreya Wagh"
date: "6/3/2018"
output:
  html_document:
    keep_md: yes
---

```{r}
Trips <- read.csv("../data/vista/2018-05-23-vista-2013-16/VISTA_2012_16_v1_SA1_CSV/T_VISTA12_16_SA1_V1.csv")
Stops <- read.csv("../data/vista/2018-05-23-vista-2013-16/VISTA_2012_16_v1_SA1_CSV/S_VISTA12_16_SA1_V1.csv")
Person <- read.csv("../data/vista/2018-05-23-vista-2013-16/VISTA_2012_16_v1_SA1_CSV/P_VISTA12_16_SA1_V1.csv")
```


```{r}
library(ggplot2)
table(Stops$DESTPURP1)
NonProf <- subset(Stops, Stops$DESTPURP1 == "Other Purpose" | Stops$DESTPURP1 == "Personal Business" | Stops$DESTPURP1 == "Pick-up or Deliver Something" | Stops$DESTPURP1 == "Recreational" | Stops$DESTPURP1 == "Social" | Stops$DESTPURP1 == "Buy Something")
NonProf <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]<2,]
NonProf$DESTPURP2 <- as.factor(as.character(NonProf$DESTPURP2))
# NonProf <- NonProf[, c(10,52,53,59,60,64,68,69,70,23,95)]
table(NonProf$DESTPURP2)
NonProfMaj <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]<1000,]
NonProfMin <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]>1000,]
NonProfMaj$DESTPURP2 <- as.factor(as.character(NonProfMaj$DESTPURP2))
NonProfMin$DESTPURP2 <- as.factor(as.character(NonProfMin$DESTPURP2))

```



```{r}
table(Trips$DESTPURP1)
NonProf <- subset(Trips, Trips$DESTPURP1 == "Other Purpose" | Trips$DESTPURP1 == "Personal Business" | Trips$DESTPURP1 == "Pick-up or Deliver Something" | Trips$DESTPURP1 == "Recreational" | Trips$DESTPURP1 == "Social" | Trips$DESTPURP1 == "Buy Something")
NonProf <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]<2,]
NonProf$DESTPURP2 <- as.factor(as.character(NonProf$DESTPURP2))
table(NonProf$DESTPURP2)
NonProfMajT <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]<1000,]
NonProfMinT <- NonProf[!table(NonProf$DESTPURP2)[NonProf$DESTPURP2]>1000,]
```




```{r, fig.width=15, fig.height=10}
ggplot(NonProfMin, aes(x=NonProfMin$DESTPURP2, fill = NonProfMin$SEX)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2, fill = NonProfMaj$SEX)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2, fill = NonProfMaj$TRAVDOW)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMin, aes(x=NonProfMin$DESTPURP2, fill = NonProfMin$TRAVDOW)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2, fill = NonProfMaj$MAINMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMin, aes(x=NonProfMin$DESTPURP2, fill = NonProfMin$MAINMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2, fill = NonProfMaj$AGEGROUP)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMin, aes(x=NonProfMin$DESTPURP2, fill = NonProfMin$AGEGROUP)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

pubmaj <- subset(NonProfMaj[(NonProfMaj$MAINMODE != "Vehicle Driver"& NonProfMaj$MAINMODE != "Vehicle Passenger" & NonProfMaj$MAINMODE!= "Walking"),])
ggplot(pubmaj, aes(x=pubmaj$DESTPURP2, fill = pubmaj$MAINMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
pubmin <- subset(NonProfMin[(NonProfMin$MAINMODE != "Vehicle Driver"& NonProfMin$MAINMODE != "Vehicle Passenger" & NonProfMin$MAINMODE!= "Walking"),])
ggplot(pubmin, aes(x=pubmin$DESTPURP2, fill = pubmin$MAINMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
# NonProfMajTab <- as.data.frame(table(NonProfMaj$DESTPURP2, NonProfMaj$SEX, NonProfMaj$Isweekend))
# #For Average Day
# as.integer(NonProfMajTab$Freq)
# NonProfMajTab$Freq[NonProfMajTab$Var3 == "Weekend"] <- (NonProfMajTab$Freq/2)

```
There is a major issue in all Mode type plots we have made. When we consider MainMode, it may not be the actualy major mode he has taken. For example, the reason trams have totally disappeared in these plots is because all trams are used as a Change Mode purpose. Before and after a tram station, there is some walking/driving to get from and to locations. We need to find the 'Main' mode of transport used. We will need to somehow focus on Trips and Stops together for the same. 


```{r, fig.width=15, fig.height=10}
ggplot(NonProfMajT, aes(x=NonProfMajT$DESTPURP2, fill = NonProfMajT$LINKMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMinT, aes(x=NonProfMinT$DESTPURP2, fill = NonProfMinT$LINKMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
pubmajT <- subset(NonProfMajT[(NonProfMajT$LINKMODE != "Vehicle Driver"& NonProfMajT$LINKMODE != "Vehicle Passenger" & NonProfMajT$LINKMODE!= "Walking"),])
ggplot(pubmajT, aes(x=pubmajT$DESTPURP2, fill = pubmajT$LINKMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
pubminT <- subset(NonProfMinT[(NonProfMinT$LINKMODE != "Vehicle Driver"& NonProfMinT$LINKMODE != "Vehicle Passenger" & NonProfMinT$LINKMODE!= "Walking"),])
ggplot(pubminT, aes(x=pubminT$DESTPURP2, fill = pubminT$LINKMODE)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r, fig.width=15, fig.height=10}
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2 ,y=NonProfMaj$STARTIME, fill = NonProfMaj$SEX)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
NonProfMaj$DURATION <- as.numeric(as.character(NonProfMaj$DURATION))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2 ,y=NonProfMaj$DURATION, fill = NonProfMaj$SEX)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProfMaj, aes(x=NonProfMaj$DESTPURP2 ,y=NonProfMaj$VISTADIST, fill = NonProfMaj$SEX)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r, fig.width=15, fig.height=10}
NonProf$Isweekend <- ifelse(NonProf$TRAVDOW == "Sunday" | NonProf$TRAVDOW == "Saturday", "Weekend", "Weekday")
NonProf$IsweekendWt <- ifelse(NonProf$TRAVDOW == "Sunday" | NonProf$TRAVDOW == "Saturday", 0.5, 0.2)
table(NonProf$DESTPURP2, NonProf$Isweekend)
ggplot(NonProf, aes(x=NonProf$DESTPURP2, fill = NonProf$Isweekend)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(NonProf, aes(x=NonProf$DESTPURP2, fill = NonProf$Isweekend, weight = NonProf$IsweekendWt)) + geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

